Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-02 phd/dissertation/chapter5.tex
giving up on rewrite of main proof

@@

\section{$k+1$-tactics and marks for $\gruKPGame{X}$}

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a space $\mb X$ for which
$\pl K\win\gruKPGame{\mb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\mb X}$
for any $k<\omega$.

\begin{defn}
  An $L$-space is a herditarally Lindel\"of, non-separable space.
\end{defn}

\begin{thm}
  Under $CH$(?), there exists a zero-dimensional, compact $L$-space.
  Furthermore, there exists a point-countable collection of clopen sets
  $\mc U=\{U_\alpha:\alpha<\omega_1\}$ in $X$ such
  that every point-finite subcollection of $\mc U$ is countable.
\end{thm}

\begin{proof}
  (TODO or find citation)
\end{proof}

\begin{defn}
  Let $\mb X=(X\times 2^{<\omega})\cup 2^\omega$ denote a Cantor tree
  of zero-dimensional, compact $L$-spaces $X$ with a point-countable collection
  of clopen sets $\mc U=\{U_\alpha:\alpha<\omega_1\}$ such
  that every point-finite subcollection of $\mc U$ is countable.
  The topology on $\mb X$ is
  given by decaring $U\times\{s\}$ to be an open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be an open
  neighborhood of $f\in 2^\omega$ for each $\alpha<\omega_1$ and $m<\omega$.
\end{defn}

% \section{Cantor tree space example}

% \begin{ex}
%   Let $X$ be a zero-dimensional, compact L-space
%   (hereditarally Lindeloff and non-separable).
%   It is a fact that there exists a point-countable collection
%   $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
%   also true that any point-finite subcollection of $\mathcal{U}$ is countable.

%   Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
%   Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
%   $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

%   Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
%   tree of $2^{<\omega}$ copies of $X$, and where
%   \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
%   is an open set about each $c_\alpha$.
% \end{ex}

% \begin{prop}
% $K \win \gruKPGame{\mathbb{X}}$.
% \end{prop}

% \begin{thm}(cor of G, game-theoretic proof by me)
% $K\not\tactwin\gruKPGame{\mathbb{X}}$.
% \end{thm}

% \begin{thm}
% $K\not\ktactwin{k}\gruKPGame{\mathbb{X}}$.
% \end{thm}

>>>>

The following result was observed in \cite{MR540599}; a proof is provided
for convenience.

@@

\section{Tactics and marks for $\gruKPGame{X}$}

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a space $\pmb X$ for which
$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\pmb X}$
for any $k<\omega$.

\begin{thm}
  There exists a compact, zero-dimensional topological space $X$
  such that $X$ has a point-countable cover
  $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct clopen sets.
\end{thm}

\begin{proof}
  (TODO)
\end{proof}

\begin{defn}
  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
  clopen sets which is not $\sigma$-point-finite, along with an uncountable
  subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\pmb X$ is
  given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $B_{\alpha,n}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
  $m<\omega$.
\end{defn}

\begin{defn}
  Let $F\in \omega_1^{<\omega}$ and $m,n<\omega$.
  \[
    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
  \]
  \[
    a_n = \{\<i,0\>:i<n\}\cup\{\<n,1\>\}
  \]
  \[
    A = \{a_n : n<\omega\}
  \]
  \[
    K_F' = K_F \setminus (X \times A)
  \]
  \[
    L_m = X \times 2^{<m}
  \]
\end{defn}

\begin{lem}
  Then $K_F$, $K_F'$, $L_m$ are compact in $\pmb X$.
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lem}

\begin{proof}
  $K_F$ contains $C_F=\{c_\alpha: \alpha\in F\}\subseteq C$, so any
  cover of basic open sets must include $B_{\alpha,n_\alpha}$ for each
  $\alpha\in F$, and the remaining uncovered portion of $K_F$ is a closed
  subset of a finite union of copies of compact $X$. Then $K_F'$ is also
  compact as it is a closed subset of $K_F$, and $L_m$ is compact as it
  is a finite union of copies of compact $X$.

  Let $D$ be compact. Consider the open cover
    \[
      \{
        B_{\alpha,0}
      :
        \alpha<\omega_1
      \}
      \cup
      \{
        X\times\{s\}
      :
        s\in 2^{<\omega}
      \}
    \]
  and note that the finite subcover for $D$ contains subsets of some
  $K_F' \cup L_m$.
\end{proof}

\begin{thm}
  $\pl K\win\gruKPGame{\pmb X}$.
\end{thm}

\begin{proof}
  Since $\{U_\alpha:\alpha<\omega_1\}$ is a point-countable cover,
  for each $x\in X$ let $\alpha_{x,n}<\omega_1$ yield
  ordinals such that $x\in U_{\alpha_{x,n}}$ for $n<\omega$.

  Let $M:\pmb X\times \omega\to \mc K(\pmb X)$ as follows:
    \[
      M(\pmb x,n)
        =
      \left\{
        \begin{array}{lcl}
          K_{\{\alpha_{x,m}:m\leq n\}}
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          K_{\{\alpha\}}
        & : &
          \pmb x = c_\alpha \in C
        \end{array}
      \right.
    \]
  and use $M$ to define the strategy $\sigma$ for each $\pmb a\in\pmb X^{<\omega}$:
    \[
      \sigma(\pmb a)
        =
      L_{|\pmb a|}
        \cup
      \bigcup_{i< |\pmb a|}
      M(\pmb a(i),|\pmb a|)
    \]

  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\sigma$. Then as
  $\pmb p(n)\not\in L_n$, for each $\pmb x=\<x,s\>\in X\times 2^{<\omega}$,
  $X\times\{s\}$ is an open neighborhood of $\pmb x$ which contains finitely
  many $\pmb p(n)$.

  Then consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
  Then if $\pmb p(n)=\<x,s\>$ with $\alpha = \alpha_{x,N}$ for some $N<\omega$,
  then $\pmb p(m)\not\in B_{\alpha,0}$ for $\max(n,N)<m<\omega$.
  Or, if $\pmb p(n)=c_\alpha$, then
  $\pmb p(m)\not\in B_{\alpha,0}$ for $n<m<\omega$.
  Otherwise, $\pmb p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
  In any case, $B_{\alpha,0}$ is a neighborhood of $\pmb x$ which contains finitely
  many $\pmb p(n)$. Therefore, $\sigma$ is a winning strategy.
\end{proof}

We will show that there does not exist any winning $k$-Markov strategy for
$\pl K$ in this game. Knowledge of round number does not assist $\pl K$,
since she may force $\pl P$ to either stay within $C$, or to seed a growing
integer by forcing her to play outside $L_{|s|+1}$ in response to
$\<x,s\>\in X\times 2^{<\omega}$.

\begin{lem}
  If $\pl K\kmarkwin{k+1}\gruKPGame{\pmb X}$, then
  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  Let $\sigma$ be a winning $k+1$-mark for $\pl K$ such that $m\leq n$ and
  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  For a sequence $p$, let $p\rest^k n=\nu_k(p\rest n)$ give the last $k$
  terms of $p\rest n$.

  Define $r:\pmb X\to\omega$ by
    \[
      r(\pmb x)
        =
      \left\{
        \begin{array}{lcl}
          |s|
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          0
        & : &
          \pmb x \in C
        \end{array}
      \right.
    \]
  and use $r$ to define the $k+1$-tactic $\tau$ by
    \[
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]
    \[
      \tau(\pmb t\concat\<\pmb x\>)
        =
      L_{r(\pmb x)+1}
        \cup
      \{\pmb x\}
        \cup
      \sigma(\pmb t\concat\<\pmb x\>,r(\pmb x)+1)
    \]

  Let $\pmb p:\omega\to\pmb X$ be a legal attack by $\pl P$ against $\tau$.
  If $\pmb p(n)\in C$ for $N<n<\omega$, then since no $\pmb p(n)$ may be legally
  repeated, $\{\{\pmb p(n)\}:N<n<\omega\}$ is a discrete collection, making
  $\{\{\pmb p(n)\}:n<\omega\}$ locally finite.

  Otherwise, let $f\in\omega^\omega$ be increasing and define
  $\pmb q:\omega\to X\times 2^{<\omega}$ such that $\pmb q(i)=\pmb p(f(i))$,
  and $\pmb p(j)\in X\times 2^{<\omega}$ implies there is some $i$ with $j=f(i)$.
  It follows that
    \[
      \pmb q(0)
        =
      \pmb p(f(0))
        \not\in
      \bigcup_{m\leq f(0)}\tau(\pmb p \rest^{k+1} m)
        \supseteq
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]

  Denoting $\pmb q(n)=\<x_n,s_n\>$, it's trivial to note that $|s_0|\geq 0$.
  Assuming that $|s_m|\geq m$ for $m\leq n$,
  it then follows that
    \[
      \pmb q(n+1)
        =
      \pmb p(f(n+1))
        \not\in
      \bigcup_{m\leq f(n+1)}\tau(\pmb p\rest^{k+1} m)
    \]
    \[
        \supseteq
      \bigcup_{m\leq n}\tau(\pmb q\rest^{k+1} m)
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),|s_m|+1)
    \]
    \[
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),m+1)
    \]
  and
    \[
      \pmb q(n+1)
        \not\in
      \tau(\pmb q\rest^{k+1} (n+1))
        \supseteq
      L_{r(\pmb q(n))}
        =
      L_{|s_n|+1}
    \]
  gives $|s_{n+1}|\geq|s_n|+1\geq n+1$.
  Thus $\pmb q$ is a legal attack on the winning $k+1$-Markov strategy
  $\sigma$, so the collection $\{\{\pmb q(n)\}:n<\omega\}$ is locally finite.
  and it follows that $\{\{\pmb p(n)\}:n<\omega\}$ is also locally finite.
\end{proof}

\begin{lem}
  If $\pl K\ktactwin{k+2}\gruKPGame{\pmb X}$, then
  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  \newcommand{\hi}{\text{height}}
  \newcommand{\de}{\text{depth}}
  Fix an arbitrary $y\in X$. For $\pmb t\in \pmb X^{<\omega}$, define the
  following:
    \begin{itemize}
      \item $\hi(\pmb t)<\omega$ satisfying
            $|s|\leq \hi(\pmb t)$ for each
            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
      \item $\de(\pmb t)\in [X]^{<\omega}$ satisfying
            $x\in\de(\pmb t)$ for each
            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
      % \item $\pmb R(\pmb t)\in [\pmb X^{<\omega}]^{<\omega}$ such that
      %       $\pmb r\in \pmb R(\pmb t)$
      %       satisfies one of the following:
      %   \begin{itemize}
      %     \item $\pmb r(i)=c$ where $c\in C\cap\ran{\pmb t}$
      %     \item $\pmb r(i)=\<x,s\>$ where $s\leq\hi(\pmb t)$,
      %                                     $x\in\de(\pmb t)$
      %     \item $\pmb r(i)=\<y,s\>$ where $s\leq\hi(\pmb t)$
      %   \end{itemize}
    \end{itemize}

  For each compact set $C$, define $F(C)\in[\omega_1]^{<\omega}$ and
  $m(C)<\omega$ such that $C\subseteq K'_{F(C)}\cup L_{m(C)}$.

  Let $\sigma$ be a winning $k+2$-tactic for $\pl K$.
  For $\pmb t\in \pmb X^{<\omega}$, let $\pmb r\preceq \pmb t$ denote that
  $\pmb r$ is a subsequence of a permutation of $\pmb t$, and let
  $\pmb r\preceq_i \pmb t$ denote that $\pmb r$ is a subsequence of a
  permutation of $\pmb t\concat\<\<y,s\>\>$ for some $s\in 2^{\leq i}$.

  Let $M(\pmb t)=\max_{\pmb r\preceq \pmb t} m(\sigma(\pmb r\rest^{k+2}))$.
  We construct a $k+1$-tactic $\tau$ for $\pl K$ as follows:
    \[
      \tau(\pmb t)
        =
      \bigcup_{\pmb r\preceq_{|M(\pmb t)|} \pmb t}
      \sigma(\pmb r)
    \]
  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\tau$, so
    \[
      \pmb p(n)
        \not\in
      \bigcup_{m\leq n}
      \tau(\pmb p\rest^{k+1} m)
    \]
  Define the attack $\pmb q:\omega\to\pmb X$ as follows for $i<\omega$,
  $j<k+1$:
    \[
      \pmb q((k+2)i+j) = \pmb p((k+1)i+j)
    \]
    \[
      \pmb q((k+2)i+(k+1)) = \<y,a_{|M()|}\>
    \]

\end{proof}

% \begin{prop}
% $K \win \gruKPGame{\pmb X}$.
% \end{prop}

% \begin{thm}(cor of G, game-theoretic proof by me)
% $K\not\tactwin\gruKPGame{\pmb X}$.
% \end{thm}

% \begin{thm}
% $K\not\ktactwin{k}\gruKPGame{\pmb X}$.
% \end{thm}
